Ensembler: Enabling high-throughput molecular simulations at the superfamily scale

### 2015-04-03 manuscript/ms.tex
Various updates

{\color{red}[JDC: This section looks pretty anemic.  What other kinds of analyses can we do for all the TKs?  There is so much data here!  There must be something neat we can do to examine it, right?]}

{\color{blue}[DLP: for further analysis, a good option might be to try to make a more rigorous assessment of model quality via comparison to reference crystal structures, based on features such as RMSD, phi/psi angles, H-bonds etc.
We could also try using the Rosetta heuristic scoring function for this purpose.]}

@@

{\color{red}[JDC: In the Discussion, let's be sure to talk about the limitations and what could be improved or added in the future.  For example, we don't yet handle counterions (e.g.~structural Zn$^{2+}$), prosthetic groups (e.g.~heme), or cofactors (e.g.~ATP) yet.  We don't handle post-translational modifications either (such as phosphorylation, methylation, glycosylation, etc.).  It's a good idea to suggest that this is an important first step toward enabling superfamily- and genomics-scale modeling, but there's a lot of work yet to be done.]}

@@

Some amino acids can exist in different protonation states, depending on pH and on their local environment.
These protonation states can have important effects on biological processes.
For example, long timescale MD simulations have suggested that the conformation of the DFG motif of the TK Abl1---believed to be an important regulatory mechanism [CITE: Abl1 DFG flip evidence]---is controlled by protonation of the aspartate~\cite{shan:pnas:2009:abl}.
Currently, protonation states are assigned simply based on pH (a user-controllable parameter).
At neutral pH, histidines have two protonation states which are approximately equally likely, and in this situation the selection is therefore made based on which state results in a better hydrogen bond.
It would be highly desirable to instead use a method which assigns amino acid protonation states based on a rigorous assessment of the local environment.
We thus plan to implement an interface and command-line function for assigning protonation states with MCCE2~\cite{alexov-gunner:biophys-j:1997:mcce2,georgescu-alexov-gunner:biophys-j:2002:mcce2,song-mao-gunner:j-comput-chem:2009:mcce2}, which uses electrostatics calculations combined with Monte Carlo sampling of side chain conformers to calculate pKa values.
{\color{red}[JDC: I think we may want to consider doing that at this stage.  Let's discuss.]}

>>>>

@@

@@

Some amino acids can exist in different protonation states, depending on pH and on their local environment.
These protonation states can have important effects on biological processes.
For example, long timescale MD simulations have suggested that the conformation of the DFG motif of the TK Abl1---believed to be an important regulatory mechanism [CITE: Abl1 DFG flip evidence]---is controlled by protonation of the aspartate~\cite{shan:pnas:2009:abl}.
Currently, protonation states are assigned simply based on pH (a user-controllable parameter).
At neutral pH, histidines have two protonation states which are approximately equally likely, and in this situation the selection is therefore made based on which state results in a better hydrogen bond.
It would be highly desirable to instead use a method which assigns amino acid protonation states based on a rigorous assessment of the local environment.
We thus plan to implement an interface and command-line function for assigning protonation states with MCCE2~\cite{alexov-gunner:biophys-j:1997:mcce2,georgescu-alexov-gunner:biophys-j:2002:mcce2,song-mao-gunner:j-comput-chem:2009:mcce2}, which uses electrostatics calculations combined with Monte Carlo sampling of side chain conformers to calculate pKa values.
